Data Prep: IUCN and AquaMaps

### 2017-03-08 data_explore/data_prep.Rmd
checking the name matching

### some confusion due to non-matching scinames and IDs...
spp_all <- spp_all %>%
  mutate(iucn_match = iucn_sid == iucn_id,
         iucn_wrong_map = ifelse(!iucn_match & iucn_id %in% spp_all$iucn_sid, TRUE, FALSE)) %>%
  mutate(iucn_sid = ifelse(iucn_wrong_map & !is.na(iucn_wrong_map), iucn_id, iucn_sid)) %>%
  select(-iucn_match, -iucn_wrong_map, -iucn_id, -sciname_count) %>%
  distinct()

length(unique(x$iucn_sid)) ###  4013, incl NA
length(unique(x$am_sid))   ### 22890, incl NA

>>>>

### some confusion due to non-matching scinames and IDs...
spp_all <- spp_all %>%
  mutate(iucn_match = iucn_sid == iucn_id,
         iucn_wrong_map = ifelse(!iucn_match & iucn_id %in% spp_all$iucn_sid, TRUE, FALSE)) %>%
  mutate(iucn_sid = ifelse(iucn_wrong_map & !is.na(iucn_wrong_map), iucn_id, iucn_sid)) %>%
  # select(-iucn_match, -iucn_wrong_map, -iucn_id, -sciname_count) %>%
  distinct()

# length(unique(spp_all$iucn_sid)) ###  4013, incl NA
# length(unique(spp_all$am_sid))   ### 22890, incl NA
# qwer <- spp_all %>% filter(!is.na(iucn_sid) & !is.na(am_sid))
# length(unique(qwer$iucn_sid)) ### 2320
# length(unique(qwer$am_sid)) ### 2314
# length(qwer %>% filter(iucn_match) %>% .$iucn_sid %>% unique()) ### 1852
# 
# x <- spp_iucn_maps %>%
#   rename(iucn_sciname = sciname) %>%
#   full_join(spp_am_maps %>% 
#               rename(am_sciname = sciname), 
#             by = c('iucn_sid' = 'iucn_id')) %>%
#   select(iucn_sid, iucn_sciname, am_sid, am_sciname) %>%
#   mutate(name_match = iucn_sciname == am_sciname) %>%
#   distinct()
# asdf <- x %>% filter(!is.na(iucn_sid) & !is.na(am_sid)) %>%
#   filter(!is.na(iucn_sciname) & !is.na(am_sciname))
# length(unique(asdf$iucn_sid))
# length(unique(asdf$am_sid))
